Online {\IterComp}

### 2017-09-13 motivation.tex
updates figure with WPO-R2

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.5\textwidth]{figs/motivation-online.pdf}
    \caption{Histograms of speedup over \texttt{-O3} for each of the 1,000 inputs of XXX. The green histogram shows the speedup when using
    the optimization sequence selected by offline \itercomp, the blue one is the speedup using the optimization sequence selected by an
    online-like approach.}
    \label{fig:motivation-online}
\end{figure}

To show this, we performed offline \itercomp on XXX using a small subset of its inputs and we identified the optimization sequence that
maximizes performance. In Figure~\ref{fig:motivation-online}, the green bars are the histogram of speedups compared to \texttt{-O3} for
every individual input, while the dark green line shows the speedup averaged over all inputs. Despite the selected optimization sequence
being the best for some inputs, we see that on average it improves performance by only 6\% and hurts performance for almost half the
inputs. Just randomly choosing an input set for offline \itercomp can be counterproductive.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.5\textwidth]{figs/motivation-metric.pdf}
    \caption{Relationship between IPC and execution time vs optimization speedup for XXX different binaries of XXX. Each point represents
	averages over all inputs.}
    \label{fig:motivation-metric}
\end{figure}

This is not an entirely surprising result. Evaluating our optimization decisions on more inputs decreases the chances of optimizing for an
unrepresentative input. Despite that offline \itercomp is still the preferred way. Measuring the speedup caused by an optimization requires
running the same input \textit{at least twice}, one of the optimized and one for the baseline binary. This is either infeasible or
undesirable in a realistic online \itercomp scenario. There are two existing workarounds to this problem: directly comparing the
\textit{execution time} of each run against previous runs or directly comparing the \textit{instructions per cycle}~(IPC)~\citep{fursin07}.
Neither metric is a good proxy for speedup. Figure~\ref{fig:motivation-metric} plots the measured IPC and execution time versus the real
speedup for XXX different binaries of the XXX benchmark. IPC, execution time, and speedup are averaged over all inputs. Both metrics
correlate little with speedup. Different inputs require a different amount of work which dominates the changes in execution time. IPC on
the other hand might improve with a more efficient binary but the opposite can also be true. For example, inserting \texttt{NOP} statements
will usually improve IPC.

>>>>

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.5\textwidth]{figs/motivation-online.pdf}
    \caption{Histograms of speedup over \texttt{-O3} for each of the 1,000 inputs of \texttt{susan\_c}. The green histogram shows the speedup when using
    the optimization sequence selected by offline \itercomp, the blue one is the speedup using the optimization sequence selected by an
    online-like approach.}
    \label{fig:motivation-online}
\end{figure}

To show this, we performed offline \itercomp on \texttt{susan\_c} using a small subset of its inputs and we identified the optimization sequence that
maximizes performance. In Figure~\ref{fig:motivation-online}, the green bars are the histogram of speedups compared to \texttt{-O3} for
every individual input, while the dark green line shows the speedup averaged over all inputs. Despite the selected optimization sequence
being the best for some inputs, we see that on average it improves performance by only 6\% and hurts performance for almost half the
inputs. Just randomly choosing an input set for offline \itercomp can be counterproductive.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.5\textwidth]{figs/motivation-metric.pdf}
    \caption{Relationship between IPC and execution time vs optimization speedup for 500 different binaries of \texttt{susan\_c}. Each point represents
	averages over a distinct subsets of its inputs.}
    \label{fig:motivation-metric}
\end{figure}

This is not an entirely surprising result. Evaluating our optimization decisions on more inputs decreases the chances of optimizing for an
unrepresentative input. Despite that offline \itercomp is still the preferred way. Measuring the speedup caused by an optimization requires
running the same input \textit{at least twice}, one of the optimized and one for the baseline binary. This is either infeasible or
undesirable in a realistic online \itercomp scenario. There are two existing workarounds to this problem: directly comparing the
\textit{execution time} of each run against previous runs or directly comparing the \textit{instructions per cycle}~(IPC)~\citep{fursin07}.
Neither metric is a good proxy for speedup. Figure~\ref{fig:motivation-metric} plots the measured IPC and execution time versus the real
speedup for 500 different binaries of the \texttt{susan\_c} benchmark. IPC, execution time, and speedup are averaged over distinct subsets of its inputs.
Both metrics have no direct correlation with speedup. Different inputs require a different amount of work which dominates the changes in execution time. IPC on
the other hand might improve with a more efficient binary but the opposite can also be true. For example,
replacing many one-cycle instructions by fewer multi-cycle instructions.
%inserting \texttt{NOP} statements will usually improve IPC.
